GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis - sensitivity analysis

### 2024-01-02 figs/GSE158422_sensitivity.Rmd
figs

@@

@@

@@

>>>>

pdf("fig3c.pdf",height=6,width=7)
par(mar = c(5.1, 29.1, 4.1, 2.1))
barplot(abs(top$s.dist),horiz=TRUE,las=1,names.arg=barnames, cex.names=0.8,
  cex.axis=0.8,col=cols, xlab="Enrichment score",main="Reactomes")
grid()
dev.off()

@@

pdf("fig3d.pdf",height=6,width=7)
par(mar = c(5.1, 29.1, 4.1, 2.1))
barplot(abs(gsiges$ES)-1,horiz=TRUE,las=1,names.arg=barnames, cex.names=0.8,
  cex.axis=0.85, col=cols, xlab="Enrichment score",main="GSA")
grid()
dev.off()

@@

pdf("fig3a.pdf",height=4,width=5)
plot(euler(v1),quantities = TRUE)
dev.off()

@@

pdf("fig3b.pdf",height=4,width=5)
boxplot(mylist,cex=0, ylab="gene set size",names=c(GSANAME,LAMNAME))
beeswarm(mylist,pch=19,add=TRUE,cex=0.3)
dev.off()
